An empirical assessment of strategies to model opponent effects in crash severity analysis

### 2020-01-16 Interactions-Crash-Severity-v1/Interactions-Crash-Severity-Title-Page-v1.tex
Completed work with Model 3 Ensemble

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={An assessment of strategies to model opponent effects in crash severity analysis},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)
% Pandoc header
\usepackage[margin=1in]{geometry}

@@

  \title{An assessment of strategies to model opponent effects in crash severity
analysis}
    \author[]{Antonio Paez\corref{c1}}
   \ead{paezha@mcmaster.ca} 
   \cortext[c1]{Corresponding Author}
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu}

    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca}

    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca}

      \address[McMaster University]{McMaster Institute for Transportation and Logistics, 1280 Main Street
West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Baton Rouge,
Louisiana, USA 70803}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={An empirical assessment of strategies to model opponent effects in crash severity analysis},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% Pandoc header
\usepackage[margin=1in]{geometry}

@@

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[]{Antonio Paez\corref{Corresponding Author}}
   \ead{paezha@mcmaster.ca} 
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu} 
    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca} 
    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca} 
      \address[McMaster University]{McMaster Institute for Transportation and Logistics, 1280 Main Street
West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Baton Rouge,
Louisiana, USA 70803}
